Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-04-26 manuscript/manuscript.Rmd
updates ms figures and figure scripts; adds ipm mean forecast horizon results

Results
-------
```{r pvalues, echo=FALSE, eval=TRUE}
##  IPM results
# Read in data
setwd("/Users/atredenn/Repos/MicroMesoForecast/manuscript/")
ipm_onestep <- readRDS("../analysis/ipm/simulations/results/one_step_validation/ipm_loyo_forecasts_combined.rds")
# Remove predictions >1 for fair comparison to [0,1] truncated quad model
resets <- which(ipm_onestep[,"cover.t1"]>1)
ipm_onestep[resets, "cover.t1"] <- 1
# Average predictions over quad-year reps
avg_ipm <- ddply(ipm_onestep, .(species, quad, t1), summarise,
                 avg_prediction = median(cover.t1),
                 observation = mean(cover.t0),
                 quant_dist = quantile(cover.t1*100, probs = 0.95) - quantile(cover.t1, probs = 0.05))
# Calculate error
avg_ipm$error <- avg_ipm$observation*100 - avg_ipm$avg_prediction*100
# Aggregate over species
ipmstats <- ddply(avg_ipm, .(species), summarise,
                  mae = mean(abs(error)),
                  mean_cover = mean(observation*100),
                  quant_dist = mean(quant_dist))
ipmstats$model <- "IPM"

##  QBM results
# Read in data
qbm_onestep <- readRDS("../analysis/quadBM/simulations/results/one_step_validation/qbm_one-step_forecasts_combined.rds")
# Average predictions over quad-year reps
avg_qbm <- ddply(qbm_onestep, .(species, quad, year), summarise,
                 avg_prediction = median(cover.t1),
                 observation = mean(cover.t0),
                 quant_dist = quantile(cover.t1*100, probs = 0.95) - quantile(cover.t1, probs = 0.05))
# Calculate error
avg_qbm$error <- avg_qbm$observation*100 - avg_qbm$avg_prediction*100
# Aggregate over species
qbmstats <- ddply(avg_qbm, .(species), summarise,
                  mae = mean(abs(error)),
                  mean_cover = mean(observation*100),
                  quant_dist = mean(quant_dist))
qbmstats$model <- "QBM"

mae_list <- list()
mae_pvals <- list()
species <- unique(qbmstats$species)
for(spp in species){
  tmp1 <- subset(avg_ipm, species==spp)
  tmp2 <- subset(avg_qbm, species==spp)
  err1 <- as.data.frame(abs(tmp1$observation - tmp1$avg_prediction))
  err2 <- as.data.frame(abs(tmp2$observation - tmp2$avg_prediction))
  colnames(err1) <- "resid"
  err1$model <- "ipm"
  colnames(err2) <- "resid"
  err2$model <- "qbm"
  errd <-  rbind(err1, err2)
  mae_ttest <- with(errd, t.test(resid~model, alternative = "less"))
  mae_list[[spp]] <- mae_ttest
  mae_pvals[[spp]] <- mae_ttest[["p.value"]]
}

mae_ps <- melt(mae_pvals)
```

### Comparison of forecast models

@@

```{r get_results, echo=FALSE, eval=FALSE}
setwd("~/Repos/MicroMesoForecast/analysis/")

####
##  Mean parameter runs
####
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/climchange_meanparams/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]

newd <- data.frame(cover=NA, species=NA, 
                   climsim=NA, model=NA, obscover=NA)
for(dospp in unique(meanparam_ipm$species)){
  tmp <- subset(meanparam_ipm, species==dospp)
  obscover <- subset(tmp, climsim=="obs")["cover"]
  tmp2 <- subset(tmp, climsim!="obs")
  tmp2$obscover <- rep(obscover$cover, times = length(unique(tmp2$climsim)))
  newd <- rbind(newd, tmp2)
}
ipm_meansims <- newd[2:nrow(newd),]
ipm_meansims$propdiff <- with(ipm_meansims, log(cover*100)-log(obscover*100))

##  QBM
meanparam_qbm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
path <- "./quadBM/simulations/results/climatechange_meanparams/"
qbmfiles_mean <- list.files(path)
for(file in qbmfiles_mean){
  tmp <- readRDS(paste(path,file,sep=""))
  tmp$model <- "QBM"
  meanparam_qbm <- rbind(meanparam_qbm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_qbm <- meanparam_qbm[2:nrow(meanparam_qbm),]

newd <- data.frame(cover=NA, species=NA, 
                   climsim=NA, model=NA, obscover=NA)
for(dospp in unique(meanparam_qbm$species)){
  tmp <- subset(meanparam_qbm, species==dospp)
  obscover <- subset(tmp, climsim=="obs")["cover"]
  tmp2 <- subset(tmp, climsim!="obs")
  tmp2$obscover <- rep(obscover$cover, times = length(unique(tmp2$climsim)))
  newd <- rbind(newd, tmp2)
}
qbm_meansims <- newd[2:nrow(newd),]
qbm_meansims$propdiff <- with(qbm_meansims, log(cover*100)-log(obscover*100))

##  Merge IPM and QBM mean parameter results
bothmodel_outs <- rbind(ipm_meansims, qbm_meansims)
meanparam_agg <- ddply(bothmodel_outs, .(species, climsim, model), summarise,
                       meandiff = mean(propdiff),
                       hidiff = quantile(propdiff, probs = 0.95),
                       lodiff = quantile(propdiff, probs = 0.05))
setwd("~/Repos/MicroMesoForecast/manuscript")
```

```{r comment_out, echo=FALSE, eval=FALSE}
# Equilibrium cover from both models was sensitive to climate (Fig. 3a-d). The IPM projected percent changes in equilibrium cover from `r round(min(subset(meanparam_agg, species=="BOGR" & model=="IPM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="BOGR" & model=="IPM")["meandiff"])*100)`% for *B. gracilis*, `r round(min(subset(meanparam_agg, species=="HECO" & model=="IPM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="HECO" & model=="IPM")["meandiff"])*100)`% for *H. comata*, `r round(min(subset(meanparam_agg, species=="PASM" & model=="IPM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="PASM" & model=="IPM")["meandiff"])*100)`% for *P. smithii*, and `r round(min(subset(meanparam_agg, species=="POSE" & model=="IPM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="POSE" & model=="IPM")["meandiff"])*100)`% for *P. secunda*. The QBM projected opposite and greater percent changes in equilibrium cover for *B. gracilis* (`r round(min(subset(meanparam_agg, species=="BOGR" & model=="QBM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="BOGR" & model=="QBM")["meandiff"])*100)`%) and *H. comata* (`r round(min(subset(meanparam_agg, species=="HECO" & model=="QBM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="HECO" & model=="QBM")["meandiff"])*100)`%; Fig. 3a-b). For *P. smithii*, the QBM projected opposite changes in equilibrium cover than the IPM, but of similar magnitude (`r round(min(subset(meanparam_agg, species=="PASM" & model=="QBM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="PASM" & model=="QBM")["meandiff"])*100)`%; Fig. 3c). *P. secunda* was the only species that the IPM and QBM made projections of the same sign and somewhat similar magnitude (`r round(min(subset(meanparam_agg, species=="POSE" & model=="QBM")["meandiff"])*100)` to `r round(max(subset(meanparam_agg, species=="POSE" & model=="QBM")["meandiff"])*100)`%; Fig. 3d). 
```

@@

Figure Legends
--------------
**Figure 1.** Time series of average percent cover over all quadrats for our four focal species: *Bouteloua gracilis* (BOGR), *Hesperostipa comata* (HECO), *Pascopyrum smithii* (PASM), and *Poa secunda* (POSE). Light grey lines show trajectories of individual quadrats. Note the different y-axis scales across panels.

Figure 2. Work flow of the data aggregation, model fitting, and population simulating.

Figure 3. Sensitivity of equilibrium cover simulated from the IPM to each climate scenario applied to individual and combined vital rates. For example, the points associated with G show the median cover from IPM simulations where a climate perturbation is applied only to the growth regression climate covariates. These simulations use mean parameter values for clarity.

Figure 4. Effect of quadrat sample size on the precision (standard deviation) of main climate effect estimates in the QBM. Increasing the number of quadrats results in diminishing returns in terms of parameter certainty. Light dashed lines show individual climate effects at five quadrat sample sizes. Thick dark lines are inverse gaussian fits showing the mean effect of increasing quadrat sample size on parameter precision.

Figure 5. Correlations (r) between QBM and IPM estimates of climate effects. We ignore sizeXclimate interactions since these are not directly comparable across model types. The QBM does not have multiple vital rates, so its values are repeated across panels within each species. Across top panels, 'growth' = growth regression, 'rec' = recruitment regression, 'surv' = survival regression.

Figure 6. Mean (points) and 90% quantiles (errorbars) for the proportional difference between baseline simulations (using observed climate) and the climate pertubation simulation on the x-axis. We calculated proportional difference as log(perturbed climate cover) - log(observed climate cover), where 'perturbed' and 'observed' refer to the climate time series used to drive interannual variation in the simulations. Model error and parameter uncertainty were propagated through the simulation phase. Climate simulations are as in Figure 3.

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Time series of average percent cover over all quadrats for our four focal species: *Bouteloua gracilis* (BOGR), *Hesperostipa comata* (HECO), *Pascopyrum smithii* (PASM), and *Poa secunda* (POSE). Light grey lines show trajectories of individual quadrats. Note the different y-axis scales across panels.", fig.height=2, fig.width=8.5, eval=T}
library(ggthemes)
obs_data <- read.csv("../analysis/speciesData/quadAllCover.csv")
#remove zeros for averaging
obs_data <- obs_data[which(obs_data$propCover>0),]
avgobs <- ddply(obs_data, .(year, Species), summarise,
                mean_cover = mean(propCover))

@@

```{r figure_2,dependson="plot-options", fig.cap="Work flow of the data aggregation, model fitting, and population simulating.", fig.height=4, eval=T}
library(png)
library(grid)
img <- readPNG("components/figure/micromeso_flowchart.png")
grid.raster(img)
```

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Since our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients). Kernel bandwidths of posterior densities were adjusted by a factor of 4 for visual clarity.}
\end{figure}

@@

@@

```{r figure_5, dependson="plot-options", fig.cap="Correlations (r) between QBM and IPM estimates of climate effects. We ignore sizeXclimate interactions since these are not directly comparable across model types. The QBM does not have multiple vital rates, so its values are repeated across panels within each species. Across top panels, 'growth' = growth regression, 'rec' = recruitment regression, 'surv' = survival regression.", fig.width=6, fig.height=6, cache=FALSE, results='hide', eval=F}
##  Figure script to look at correlations between IPM and QBM
##    climate effect estimates.

library(ggmcmc)
library(gridExtra)
library(ggplot2)

allfiles <- list.files("../analysis/speciesData/")
removals <- grep("csv", allfiles)
species_list <- allfiles[-removals]

clim_covs <- c("pptLag", "ppt1", "ppt2", "TmeanSpr1", "TmeanSpr2",
               "ppt1xTmeanSpr1", "ppt2xTmeanSpr2",
               "sizeXpptLag", "sizeXppt1", "sizeXppt2",
               "sizeXTmeanSpr1", "sizeXTmeanSpr2")
clim_mains <- c("pptLag", "ppt1", "ppt2", "TmeanSpr1", "TmeanSpr2",
                "ppt1xTmeanSpr1", "ppt2xTmeanSpr2")

####
##  Get mean growth climate effects
####
growth_parms <- data.frame(species=NA, model=NA, parameter=NA, value=NA)
for(spp in species_list){
  tmp_data <- readRDS(paste("../analysis/ipm/vitalRateRegs/growth/growth_stanmcmc_", spp, ".RDS", sep=""))
  tmp_clim <- tmp_data[grep("b2", tmp_data[,"Parameter"]), ]
  tmp_clim[,"Parameter"] <- rep(clim_covs, each=3000)
  tmp_agg <- ddply(tmp_clim, .(Parameter), summarise,
                   value = median(value))
  tmp_agg2 <- tmp_agg[which(tmp_agg$Parameter %in% clim_mains), ]
  tmp_agg2$species <- spp
  tmp_agg2$model <- "ipm"
  colnames(tmp_agg2) <- tolower(colnames(tmp_agg2))
  growth_parms <- rbind(growth_parms,
                        tmp_agg2[,c("species", "model", "parameter", "value")])
}

####
##  Get mean survival climate effects
####
surv_parms <- data.frame(species=NA, model=NA, parameter=NA, value=NA)
params <- character(length = 12)
for(i in 1:12){
  params[i] <- paste("b2[",i,"]", sep="")
}
for(spp in species_list){
  tmp_data <- readRDS(paste("../analysis/ipm/vitalRateRegs/survival/survival_stanmcmc_", spp, ".RDS", sep=""))
  keeps <- which(tmp_data$Parameter %in% params)
  tmp_clim <- tmp_data[keeps, ]
  tmp_clim[,"Parameter"] <- rep(clim_covs, each=3000)
  tmp_agg <- ddply(tmp_clim, .(Parameter), summarise,
                   value = median(value))
  tmp_agg2 <- tmp_agg[which(tmp_agg$Parameter %in% clim_mains), ]
  tmp_agg2$species <- spp
  tmp_agg2$model <- "ipm"
  colnames(tmp_agg2) <- tolower(colnames(tmp_agg2))
  surv_parms <- rbind(surv_parms,
                        tmp_agg2[,c("species", "model", "parameter", "value")])
}

####
##  Get mean recruitment climate effects
####
rec_parms <- data.frame(species=NA, model=NA, parameter=NA, value=NA)
params <- character(length = 12)
for(i in 1:12){
  params[i] <- paste("b2[",i,"]", sep="")
}
for(spp in species_list){
  tmp_data <- readRDS(paste("../analysis/ipm/vitalRateRegs/recruitment/recruitment_stanmcmc_", spp, ".RDS", sep=""))
  keeps <- which(tmp_data$Parameter %in% params)
  tmp_clim <- tmp_data[keeps, ]
  tmp_clim[,"Parameter"] <- rep(clim_mains, each=3000)
  tmp_agg <- ddply(tmp_clim, .(Parameter), summarise,
                   value = median(value))
  tmp_agg2 <- tmp_agg[which(tmp_agg$Parameter %in% clim_mains), ]
  tmp_agg2$species <- spp
  tmp_agg2$model <- "ipm"
  colnames(tmp_agg2) <- tolower(colnames(tmp_agg2))
  rec_parms <- rbind(rec_parms,
                      tmp_agg2[,c("species", "model", "parameter", "value")])
}

####
##  Get QBM growth climate estimates
####
clim_covs2 <- c("pptLag", "ppt1", "ppt2", "TmeanSpr1", "TmeanSpr2",
               "ppt1xTmeanSpr1", "ppt2xTmeanSpr2",
               "coverXpptLag", "coverXppt1", "coverXppt2",
               "coverXTmeanSpr1", "coverXTmeanSpr2")

qbm_parms <- data.frame(species=NA, model=NA, parameter=NA, qbmvalue=NA)
params <- character(length = 12)
for(i in 1:12){
  params[i] <- paste("b2[",i,"]", sep="")
}
for(spp in species_list){
  tmp_data <- readRDS(paste("../analysis/quadBM/vitalRateRegressions/truncNormModel/popgrowth_stanmcmc_", spp, ".RDS", sep=""))
  keeps <- which(tmp_data$Parameter %in% params)
  tmp_clim <- tmp_data[keeps, ]
  tmp_clim[,"Parameter"] <- rep(clim_covs2, each=3000)
  tmp_agg <- ddply(tmp_clim, .(Parameter), summarise,
                   qbmvalue = median(value))
  tmp_agg2 <- tmp_agg[which(tmp_agg$Parameter %in% clim_mains), ]
  tmp_agg2$species <- spp
  tmp_agg2$model <- "qbm"
  colnames(tmp_agg2) <- tolower(colnames(tmp_agg2))
  qbm_parms <- rbind(qbm_parms,
                     tmp_agg2[,c("species", "model", "parameter", "qbmvalue")])
}

####
##  Format data, combine, and plot
####
growth_parms <- growth_parms[2:nrow(growth_parms), ]
growth_parms$vitalrate <- "growth"
surv_parms <- surv_parms[2:nrow(surv_parms), ]
surv_parms$vitalrate <- "surv"
rec_parms <- rec_parms[2:nrow(rec_parms), ]
rec_parms$vitalrate <- "rec"
ipm_parms <- rbind(growth_parms, surv_parms, rec_parms)

qbm_parms <- qbm_parms[2:nrow(qbm_parms), ]
qbm_parms$vitalrate <- "growth"
vitals <- c("surv", "rec")
qbmalone <- qbm_parms
for(dov in vitals){
  tmp <- qbmalone
  tmp$vitalrate <- dov
  qbm_parms <- rbind(qbm_parms, tmp)
}

ipm_parms <- ipm_parms[,c("species","parameter","value","vitalrate")]
qbm_parms <- qbm_parms[,c("species","parameter","qbmvalue","vitalrate")]
all_ests <- merge(ipm_parms, qbm_parms, by = c("species", "parameter", "vitalrate"))

# Calculate correlation for each group
cors <- ddply(all_ests, c("species", "vitalrate"), summarise, 
              cor = round(cor(value, qbmvalue), 2))

ggplot(all_ests, aes(x=qbmvalue, y=value))+
  geom_point(size=3)+
  geom_smooth(method="lm", color="black", fill="grey", se=FALSE)+
  facet_grid(species~vitalrate)+
  geom_text(data=cors, aes(label=paste("r = ", cor, sep="")), x=-1, y=1, size=4)+
  xlab("QBM Estimate")+
  ylab("IPM Estimate")+
  theme_bw()

setwd("~/Repos/MicroMesoForecast/manuscript/")
```

```{r figure_6, dependson="plot-options", fig.cap="Mean (points) and 90% quantiles (errorbars) for the proportional difference between baseline simulations (using observed climate) and the climate pertubation simulation on the x-axis. We calculated proportional difference as log(perturbed climate cover) - log(observed climate cover), where 'perturbed' and 'observed' refer to the climate time series used to drive interannual variation in the simulations. Model error and parameter uncertainty were propagated through the simulation phase. Climate simulations are as in Figure 3.", fig.width=4.5, fig.height=7, cache=FALSE, results='hide', eval=F}
####
##  Vary parameter runs
####
setwd("~/Repos/MicroMesoForecast/analysis/")
meanparam_ipm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
##  IPM 
path <- "./ipm/simulations/results/climchange_varyparams/"
ipmfiles_mean <- list.files(path)
ipmfiles_mean <- ipmfiles_mean[grep("cover", ipmfiles_mean)]
torm <- c(grep("10", ipmfiles_mean), grep("20", ipmfiles_mean), grep("30", ipmfiles_mean))
ipmfiles_mean <- ipmfiles_mean[-torm]
for(file in ipmfiles_mean){
  tmp <- read.csv(paste(path,file,sep=""))
  tmp$model <- "IPM"
  meanparam_ipm <- rbind(meanparam_ipm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_ipm <- meanparam_ipm[2:nrow(meanparam_ipm),]

newd <- data.frame(cover=NA, species=NA, 
                   climsim=NA, model=NA, obscover=NA)
for(dospp in unique(meanparam_ipm$species)){
  tmp <- subset(meanparam_ipm, species==dospp)
  obscover <- subset(tmp, climsim=="obs")["cover"]
  tmp2 <- subset(tmp, climsim!="obs")
  tmp2$obscover <- rep(obscover$cover, times = length(unique(tmp2$climsim)))
  newd <- rbind(newd, tmp2)
}
ipm_meansims <- newd[2:nrow(newd),]
ipm_meansims$propdiff <- with(ipm_meansims, log(cover*100)-log(obscover*100))
# ggplot(subset(ipm_meansims, species=="PASM"))+
#   geom_histogram(aes(x=cover))+
#   facet_wrap("climsim", scales = "free")+
#   scale_x_continuous(limits=c(0,0.05))
##  QBM
meanparam_qbm <- data.frame(cover=NA, species=NA, 
                             climsim=NA, model=NA)
path <- "./quadBM/simulations/results/climatechange_varyparams/"
qbmfiles_mean <- list.files(path)
for(file in qbmfiles_mean){
  tmp <- readRDS(paste(path,file,sep=""))
  tmp$model <- "QBM"
  meanparam_qbm <- rbind(meanparam_qbm, tmp[,c("cover", "species", "climsim", "model")])
}
meanparam_qbm <- meanparam_qbm[2:nrow(meanparam_qbm),]

newd <- data.frame(cover=NA, species=NA, 
                   climsim=NA, model=NA, obscover=NA)
for(dospp in unique(meanparam_qbm$species)){
  tmp <- subset(meanparam_qbm, species==dospp)
  obscover <- subset(tmp, climsim=="obs")["cover"]
  tmp2 <- subset(tmp, climsim!="obs")
  tmp2$obscover <- rep(obscover$cover, times = length(unique(tmp2$climsim)))
  newd <- rbind(newd, tmp2)
}
qbm_meansims <- newd[2:nrow(newd),]
qbm_meansims$propdiff <- with(qbm_meansims, log(cover*100)-log(obscover*100))

##  Merge IPM and QBM mean parameter results
bothmodel_outs <- rbind(ipm_meansims, qbm_meansims)

meanparam_agg <- ddply(bothmodel_outs, .(species, climsim, model), summarise,
                       meandiff = mean(propdiff),
                       hidiff = quantile(propdiff, probs = 0.95),
                       lodiff = quantile(propdiff, probs = 0.05))
dgd = position_dodge(width = 0.6)
ggplot(meanparam_agg)+
  geom_errorbar(aes(x=climsim, ymax=hidiff, ymin=lodiff, group=model, linetype=model),
                position=dgd, width=0.25)+
  geom_point(aes(x=climsim, y=meandiff, group=model, shape=model),
                position=dgd, width=0.25)+
  theme_bw()+
  scale_linetype_discrete(name="Model")+
  scale_shape_discrete(name="Model")+
  facet_wrap("species", ncol=1, scales="free")+
  scale_x_discrete(labels=c("+ppt", "+temp", "+ppt&temp"))+
  ylab("Proportional difference")+
  xlab("Climate simulation")
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
setwd("~/Repos/MicroMesoForecast/manuscript/")
```

>>>>

Results
-------
### Comparison of forecast models

@@

@@

Figures
-------
```{r figure_1, dependson="plot-options", fig.cap="Time series of average percent cover over all quadrats for our four focal species: *Bouteloua gracilis* (BOGR), *Hesperostipa comata* (HECO), *Pascopyrum smithii* (PASM), and *Poa secunda* (POSE). Light grey lines show trajectories of individual quadrats. Note the different y-axis scales across panels.", fig.height=2, fig.width=8.5, eval=T}
library(ggthemes)
obs_data <- read.csv("../analysis/data_processing/speciesData/quadAllCover.csv")
#remove zeros for averaging
obs_data <- obs_data[which(obs_data$propCover>0),]
avgobs <- ddply(obs_data, .(year, Species), summarise,
                mean_cover = mean(propCover))

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{./components/micromeso_flowchart.png}
  \caption{Work flow of the data aggregation, model fitting, and population simulating.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[height=7in]{./components/climate_posteriors_figure.png}
  \caption{Posterior distributions of climate effects ($\boldsymbol{\beta}_C$) for each species and vital rate statistical model. Since our priors were constrained via ridge-regression, we highlight climate effects whose 80\% credible intervals do not overlap zero (red for negative coefficients, blue for positive coefficients). Kernel bandwidths of posterior densities were adjusted by a factor of 4 for visual clarity.}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/climate_effect_corplots.png}
  \caption{Correlations between QBM and IPM estimates of climate effects. We ignore sizeXclimate interactions since these are not directly comparable across model types. The QBM does not have multiple vital rates, so its values are repeated across panels within each species. Across top panels, 'growth' = growth regression, 'rec' = recruitment regression, 'surv' = survival regression.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[height=6in]{./components/climate_change_results.png}
  \caption{Mean (points) and 90\% quantiles (errorbars) for the proportional difference between baseline simulations (using observed climate) and the climate pertubation simulation on the x-axis. We calculated proportional difference as log(perturbed climate cover) - log(observed climate cover), where 'perturbed' and 'observed' refer to the climate time series used to drive interannual variation in the simulations. Model error and parameter uncertainty were propagated through the simulation phase.}
\end{figure}

@@
